Where Do Population III Stars Form?

### 2018-10-10 paper.tex
Fixing case of a bibtex entry/cite

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux. We will compare our results with this relation in future sections. \citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

>>>>

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux. We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
